We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-07 paper/paper.tex
full update

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} \\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-5}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $64\pm 12$   & $45\pm 8$    \\\hline
    $c/a$ ratio & $0.45\pm 0.04$ & $0.28\pm 0.03$ & $0.55\pm0.10$ & $0.53\pm 0.10$ \\ \hline
    $b/a$ ratio & $0.82\pm 0.06$ & $0.78\pm 0.02$ & $0.82\pm0.07$ & $0.81\pm 0.08$ \\ \hline
  \end{tabular}
  \caption{Results from observations. Mean values and standard deviations for the different
    quantities describing satellite distribution: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first colum refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data. \label{table:observations}}
\end{table*}

>>>>

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}}
    & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} &
    \multicolumn{2}{c|}{\textbf{Normalized Units}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-7}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} \\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $59\pm 3$  & $21\pm 2$  & $65\pm 12$   &
    $45\pm 8$    & $-0.48\pm 0.24$ & $-2.48\pm 0.26$\\\hline
    $c/a$ ratio & $0.45\pm 0.04$ & $0.25\pm 0.05$ & $0.55\pm0.10$ &
    $0.53\pm 0.10$ & $-1.03\pm 0.37$ & $-2.18\pm 0.42$\\ \hline
    $b/a$ ratio & $0.82\pm 0.06$ & $0.80\pm 0.04$ & $0.82\pm0.07$ &
    $0.81\pm 0.08$ & $-0.02\pm 0.82$ & $-0.13\pm 0.47$\\ \hline
  \end{tabular}
  \caption{Results from observations. Mean values and standard deviations for the different
    quantities describing satellite distribution: plane width, $c/a$
    ratio and $b/a$ ratio. 
    The first colum refers to the results from
    observational data, the second column uses the spherically
    randomized version of the observational data, the third column
    corresponds to the observational data recentered and normalized
    by the randomized values. \label{table:observations}}
\end{table*}
